%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Joshua Field - Latex Resume 
% Version 1.1 (12/13/2017)
%
% TODO:
% 1.Add double column at the bottom for projects
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{titlesec}
\pagestyle{fancy}
\fancyhf{}
%\newcommand{\address}{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Joshua}{Field}{ 
{\textcolor{black}{\href{joshafield.com}{http://joshafield.com}} | \href{mailto:joshfield999@gmail.com}{joshfield99@gmail.com} | 626.616.6321}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\runsubsection{Northeastern University}
\descript{| Candidate for BS in Electrical \& Computer Engineering}
\vspace{0.5mm} %fix for vertical space
\location{GPA: \custombold{N/A} | Graduation Date : \custombold{June 2021}}
\vspace{0.5mm}
\begin{tightemize}
\item[] \custombold{Relevant Courses:} Cornerstone 1 \& 2 | Calculus 2
\end{tightemize}
\sectionsep

\runsubsection{Arcadia High School}
\vspace{0.5mm} %fix for vertical space
\descript{}
\location{GPA: \custombold{3.93} | Graduation Date : \custombold{June 2017}}
\vspace{0.5mm}
\begin{tightemize}
\item[] \custombold{Relevant Courses:}AP Calculus AB | AP Physics C | AP Chemistry | AP Computer Science A | AP Comparative Government | AP English Literature
\item[] \custombold{SAT(old): } 2120
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Northeastern University ResMail}
\descript{| Mail Services Associate }
\location{October 2017 – December 2017 | Boston, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Sorted and delivered mail. Also audited \& updated the computerized \custombold{database.} 
\end{tightemize}
\sectionsep

\runsubsection{Arcadia High School Marching Band}
\descript{| Trumpet Section Leader }
\location{August 2016 – June 2017 | Arcadia, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Led trumpet section practices \& instructed peers and younger members. Also organized section events. 
\end{tightemize}
\sectionsep

\runsubsection{Eagle Scout}
\descript{| Troop 104 Senior Patrol \& Instructor }
\location{August 2013 – June 2017 | Arcadia, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Was awarded the rank of \custombold{Eagle Scout} in February 2017. Led multiple troop meetings of \custombold{70+ scouts.}
\end{tightemize}
\sectionsep

\runsubsection{Johns Hopkins Engineering Innovation}
\descript{| Summer Course}
\location{June 2016 – August 2016 | Pasadena, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Used \custombold{truss analysis} to create the strongest spaghetti bridge.
\item \custombold{Reverse engineered} a light sensing robot to create \custombold{logic tables} and program our own robots.
\item Created fictional \custombold{Request For Proposal} presentations.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES & AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities \& Awards}
\runsubsection{National Merit Commended Scholar}
\descript{| 2017}
\vspace{0.5mm}
\begin{tightemize}
\item[] Was awarded to the \custombold{top 3.3\%} of students nationally
\end{tightemize}
\sectionsep

\runsubsection{Varsity Soccer Goalkeeper}
\descript{| Arcadia High School 2016 - 2017}
\vspace{0.5mm}
\begin{tightemize}
\item[] Arcadia Winter Cup 2017 \custombold{Champions}
\end{tightemize}
\sectionsep

\runsubsection{3rd Degree Black Belt}
\descript{| Taekwondo June 2006 - August 2014}
\vspace{0.5mm}
\begin{tightemize}
\item[] With \custombold{100+ hours} of volunteer instruction
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS-----------SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \renewcommand{\arraystretch}{0}
% \begin{tabularx}{\textwidth}{@{}XXl@{}@{}r@{}}
% \section{Projects} & \section{Skills} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{minipage}[t]{8cm}

% \section{Projects}

% \runsubsection{Piezoelectric Keyboard}
% \descript{}
% \vspace{0.15mm}
% %\position{ } \\
% \begin{tightemize}
% \item Used \custombold{piezoelectric sensors}. Built a \custombold{full-wave diode rectifier} \& a \custombold{voltage/amperage} sensor to measure the power generated.
% \item Used \custombold{SolidWorks} and \custombold{AutoCAD} to construct the piezoelectric sensor array \& case. 
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\runsubsection{Programming}
\location{}
\vspace{0.5mm}
\begin{tightemize}
\item[] \custombold{Skilled in:} Java \textbullet{} C++ \\
\custombold{Familiar with:} Python \textbullet{} HTML \textbullet{} CSS \textbullet{} \LaTeX \textbullet{} Matlab
\end{tightemize}
\sectionsep

\runsubsection{Computer}
\location{}
\vspace{0.5mm}
\begin{tightemize}
\item[] SolidWorks \textbullet{} AutoCAD \textbullet{} Microsoft Office Suite \\
Adobe Photoshop \textbullet{} Adobe Lightroom
\end{tightemize}
\sectionsep

%\end{minipage}
%\end{tabularx}
\end{document}